\cvsect{Industry Experience}

\begin{entrylist}
    \entry
         {03/2020 -- present}
         {Assistant Platform--Infrastructure \& Quality Team.}
         {\asstauto, \google}
         {"Okay, Google, take me home."
         \noseplist{
         	\item \textbf{Implemented} and \textbf{launched} infrastructure improvement to reduce latency for tap-to-read messages.
    			\item \textbf{Designed} and \textbf{instrumented} key components of performance measurement tool.
    			\item \textbf{Implemented} and \textbf{maintained} conformance testing framework during major migration.
    			\item \textbf{Solved} critical issues as needed, e.g. enabling multi-device arbitration, etc.
    		}
         
          \onelinelist{Android, Java, Kotlin,Python}
         }
	\entry
		{04/2019 -- 03/2020}
    		{Alexa Local Search--Data, Software Development Engineer.}
    		{\alexaauto, \atoz}
    		{"Alexa, find me a coffee shop."
    		\noseplist{
    			% \item \textbf{Guided} the foundation of new team: \textbf{wrote} the team charter and \textbf{defined} team processes.
    			% \item \textbf{Acted as Scrum Master.}
    			% \item \textbf{Constructed} a new algorithm for identifying similar entities from different sources.
    			\item \textbf{Proposed} new design for our data pipeline with focus on efficiency and incremental builds.
    			\item \textbf{Mentored} intern as they implemented a POC I designed to help curate and maintain high quality data.
    			\item \textbf{Built} a viewing portal for a key resource: \textbf{reduced} cross-team friction and \textbf{eased} developer overhead.
    		}
    		
    		 \onelinelist{AWS Athena, AWS EMR, AWS S3, Python, Scala, SQL, Zeppelin}
    		 }
	\entry
		{08/2018 -- 04/2019}
    		{Alexa Local Search--Platform, Software Development Engineer.}
    		{\alexaauto, \atoz}
    		{"Alexa, how far away is the airport?"
    		\noseplist{
    			\item \textbf{Launched} product in new country: \textbf{implemented} core feature, \textbf{identified} blocking issues, and \textbf{resolved} them by working with our partner and \textbf{designing} a fall-back option.
    			\item \textbf{Integrated} a new data provider to improve the recall and ranking of a specialized category.
    		}
    		
    		\onelinelist{AWS Elastic Search, AWS DynamoDB, AWS S3, Python, Scala}
    		}
    	\entry
		{06/2017 -- 08/2017}
    		{Software Development Engineering Intern.}
    		{\avs, \atoz}
    		{\textbf{Designed} and \textbf{implemented} an automated notification service triggered by system events. 
    		\noseplist{
    			\item Service \textbf{reduced} friction between teams and \textbf{expedited} the AVS Certification Process.
    			\item \textbf{Presented} design options, \textbf{demonstrated} a working POC, and \textbf{transferred} ownership.
    		}
    		
    		\onelinelist{AWS DynamoDB, AWS SNS, AWS SQS, HTML, Java}
    		}
\end{entrylist}