%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
%\addbibresource{bibliography.bib}
\usepackage{fancyhdr}

\pagestyle{fancy}

\begin{document}
\header{Eleanor }{Nicolson}
       {Software Development Engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    248 Pamela Dr.
    Apt. 34
    Mountain View, CA 94040
    USA
    ~
    \href{mailto:mobile}{(415) 937-3240}
    \href{mailto:email1}{e.c.nicolson@gmail}
  \section{links}
    LI:\href{https://www.linkedin.com/in/e-c-nicolson}{//in/e-c-nicolson}
    GitHub:\href{https://github.com/GingerElla}{//GingerElla}
  \section{languages}
    Greek, Latin
  \section{programming}
    Python, Scala, Java, Scheme, C, Processing
  \section{tools}
    IntelliJ, Emacs, Sublime, \LaTeX
  \section{software}
    Microsoft Office Suite,
    Apple iWork
  \section{operating systems}
    Mac OS, Linux, Windows
  \section{general skills}
  	Communication, 
  	Research, Adaptability,
  	Problem Solving
\end{aside}

\section{objective}

After graduating and working at Amazon as both an intern and a full-time employee, I am looking for a new position that will allow me better growth and mentorship opportunities. I am eager to learn and excited to solve ambiguous and challenging problems within a supportive environment.

\section{education}

\begin{entrylist}
  \entry
    {2014--2018}
    {B.A. in Computer Science and B.A. in Classics}
    {\GrinnellCollege[Grinnell College]}
    {Expected graduation in May 2018. \textbf{Overall GPA:} 3.6; \\ \textbf{CS GPA:} 3.7; \textbf{Classics GPA:} 3.8}
  \entry
    {01--06 2017}
    {Associate Student, Greek and Latin}
    {University College London}
    {Semester abroad.}
  \entry
    {06--08 2015}
    {Summer Intensive Greek Workshop}
    {University of California, Berkeley}
    {Equivalent to three semesters of introductory Greek. \textbf{GPA:} 4.0}
\end{entrylist}

\section{industry}

\begin{entrylist}
  \entry
    {xx 2019--now}
    {Software Development Engineer}
    {\AlexaAuto}
    {\emph{Something}
    \begin{itemize}
    \item nothing
    \end{itemize}
    }
  \entry
    {08 2018--2019}
    {Software Development Engineer}
    {\AlexaAuto}
    {\emph{Something}
    \begin{itemize}
    \item nothing
    \end{itemize}
    }
    
\end{entrylist}

\section{research}

\begin{entrylist}
  \entry
    {11--12 2016}
    {Course Research Asst.}
    {\GrinnellCollege}
    {\emph{Researched:}
    \begin{itemize}
    \item the basic languages of weaving, crocheting, embroidery, and quilting;
    \item how we can represent these computationally;
    \item how tools manipulate and innovate on languages .
    \end{itemize}
    \emph{Created:} 
    \begin{itemize}
    \item lesson plans, homework, and readings;
    \item manual for programmed embroidery and accompanying software;
    \item packaged versions of software for the class.
    \end{itemize}}
  \entry
    {06--08 2016}
    {Research Position.}
    {\GrinnellCollege}
    {\emph{Researched the state of Computer Science outreach camps and:}
    \begin{itemize}
    \item Organized and ran a summer coding camp for middle-schoolers;
	\item Learned how to use and program an embroidery machine;
	\item Co-authored papers on our research and the camp we ran.
    \end{itemize}
    }
\end{entrylist}

\section{miscellaneous}

\begin{entrylist}
  \entry
    {08 2016}
    {Assistant Archivist.}
    {\GrinnellCollege}
    {\emph{30-hr contract job.} Formatted images for a new, online archive.}
    
  \entry
    {2015--2018}
    {Tutor: Latin, Greek, Computer Science.}
    {\GrinnellCollege}
    {Tutored students in both group and one-on-one settings.}
    
  \entry
    {2012--2018}
    {Editor.}
    {St. Ignatius College Preparatory \& Independent}
    {\emph{Editor-in-Chief, Managing Editor, independent.} Focused on stylistic, grammatical, and organizational elements.}
    
  \entry
    {2015--2016}
    {Caterer.}
    {\GrinnellCollege}
    {Prepared, served, and cleaned up catered events.}
	
\end{entrylist}

%\section{applications}
%
%\begin{entrylist}
%  \entry
%    {2012}
%    {Who did I forget ?}
%    {\href{http://whodidiforget.com}{whodidiforget.com}}
%    {Guest list recommendation for Facebook events based on friends already attending the event.}
%  \entry
%    {2011}
%    {Fellows}
%    {\href{http://fellows-exp.com}{fellows-exp.com}}
%    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
%  \entry
%    {2008}
%    {Happy Flu}
%    {\href{http://happyflu.com}{happyflu.com}}
%    {Experiment aimed to measure viral spreading of content across the blogosphere.}
%\end{entrylist}
%
\section{publications}

``Coding Artistically for Social Good: A Pilot Project for Middle-school Outreach''
        Presentation given at Grinnell College's 2016 Science Student Research Poster Session,
        September 2016, Grinnell, Iowa.

\fancyfoot[L]{Template provided by: https://www.sharelatex.com/templates/cv-or-resume/fancy-cv \\
        Further edits by: Ella Nicolson}
%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
